\documentclass{article}
\usepackage{graphicx, amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{kotex}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{physics}
\usepackage{ esint }

\textwidth 6.5 truein 
\oddsidemargin 0 truein 
\evensidemargin -0.50 truein 
\topmargin -.5 truein 
\textheight 8.5in

\DeclareMathOperator{\cc}{\mathbb{C}}
\DeclareMathOperator{\rr}{\mathbb{R}}
\DeclareMathOperator{\bA}{\mathbb{A}}
\DeclareMathOperator{\fra}{\mathfrak{a}}
\DeclareMathOperator{\frb}{\mathfrak{b}}
\DeclareMathOperator{\frm}{\mathfrak{m}}
\DeclareMathOperator{\frp}{\mathfrak{p}}
\DeclareMathOperator{\slin}{\mathfrak{sl}}
\DeclareMathOperator{\Lie}{\mathsf{Lie}}
\DeclareMathOperator{\Alg}{\mathsf{Alg}}
\DeclareMathOperator{\Spec}{\mathrm{Spec}}
\DeclareMathOperator{\End}{\mathrm{End}}
\DeclareMathOperator{\rad}{\mathrm{rad}}
\newcommand*\Laplace{\mathop{}\!\mathbin\bigtriangleup}
\newcommand{\id}{\mathrm{id}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Sch}{\mathbf{Sch}}
\newcommand{\Ring}{\mathbf{Ring}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}

\begin{document}


\title{Partial Differential Equation - HW 4}
\author{SungBin Park, 20150462} 

 \maketitle

\section*{Problem 1}
I'll use some theorem from topology and functional analysis, and I'll follow the proof in Real Analysis, Gerland B. Folland.
\begin{theorem}
(The Baire Category Theorem) Let $X$ be a complete metric space. Then,
\begin{enumerate}
\item[(a)] If $\{U_n\}_1^\infty$ is a sequence of open dense subsets of $X$, i,e, $\overline{\cup_1^\infty U_n}=X$, then $\cap_1^\infty U_n$ is dense in $X$.
\item[(b)] $X$ is not a countable union of nowhere dense sets.
\end{enumerate}
\end{theorem}
\begin{proof}
For (a), I'll show that nonempty open set $V$ in $X$ have intersection with $\cap_1^\infty U_n$ using induction. Since $U_1$ is open dense subset of $X$, $U_1\cap W$ is open and nonempty, so there exists $B(x_0, r_0)\subset U_1\cap W$ such that $0<r_0<1$. For $n>0$, choose $x_n$ and $r_n$ by follows: assume that for $j<n$, $x_j$ and $r_j$ are chosen. Then, $B(x_{n-1},r_{n-1})\cap U_n$ is nonempty and open. Choose $x_n\in B(x_{n-1},r_{n-1})\cap U_n$ and choose $0<r_n<2^{-n}$ such that $\overline{B(x_n,r_n)}\subset B(x_{n-1},r_{n-1})$. For $n,m\geq N$, $x_n,x_m\in B(x_N, r_N)$, and $r_N\rightarrow 0$ as $N\rightarrow \infty$. Therefore, $\{x_n\}$ is a Cauchy sequence in $X$ and have limit point $x\in X$. Since $x_n\in B(r_N, x_N)$ for all $n\geq N$, $x\in \overline{B(x_N, r_N)}\subset U_N\cap B(x_0, r_0)\subset U_N\cap W$ for all $N$, implying $\left(\cap_{n=1}^\infty U_n\right)\cap W\neq \phi$.

For (b), If $\{E_n\}_{n=1}^\infty$ is a sequence of nowhere dense subsets in $X$, then $\{\overline{E_n}^c\}$ are a open dense sets since for fixed $n$ and for any $x\in \overline{E}$, $B(x,r)\cap \overline{E}^c\neq \phi$ for all $r>0$. Since $\cap\left(\overline{E_n}\right)^c\neq \phi$, $\cup E_n\subset \cup \overline{E_n}\neq X$.
\end{proof}
\begin{theorem}
(Open Mapping Theorem) Let $X$ and $Y$ be Banach spaces. If $T$ is a surjective bounded linear functional from $X$ to $Y$, $T$ is a open map.
\end{theorem}
\begin{proof}
If $T(B(0, 1))$ contains a ball of radius $r>0$, $T$ is open map since for any open set $x\in U$ in $X$, it contains open ball $B(x,r)$, $r>0$ and $T(B(x,r))=T(x)+T(B(0, r))=T(x)+rT(B(0, 1))$, which is open set in $Y$ centered at $T(x)$. Therefore, I'll show that $T(B(0, 1))$ contains a ball of radius $r>0$. I'll denote $B(0,r)=B_r$.

Since $X=\cup_{n=1}^\infty B_n$ and $T$ is surjective, $Y=T(\cup_{n=1}^\infty B_n)$. If $T(B_1)$ is nowhere dense, $T(B_n)$ are nowhere dense since dialation in $Y$ induces homeomorphism. However, this is impossible by the Baire Category Theorem since $Y$ is complete. Therefore, $\overline{T(B_1)}$ contains an open ball in $Y$ and let it $B(y_0, 4r)$ for some $y_0\in Y$, $r>0$. Choose $y_1=Tx_1\in T(B_1)$ such that $\norm{y_1-y_0}\leq 2r$; then $B(y_1,2r)\subset B(y_0, 4r)\subset \overline{T(B_1)}$, so if $\norm{y}<2r$,
\begin{equation*}
y=-Tx_1+(y_1+y)\in \overline{T(-x_1+B_1)}\subset \overline{T(B_2)}.
\end{equation*}
Dividing both by $2$, we get if $\norm{y}<r$, $y\in \overline{T(B_1)}$. I need to change $\overline{T(B_1)}$ to $T(B_1)$.

As noted above, dialation induces homeomorphism, so if $\norm{y}<r/2^n$, $y\in \overline{T(B_{1/2^n})}$. Suppose that $y\in r/2$, then there exists $x_1\in B_{1/2}$ such that $\norm{y-Tx_1}\leq r/4$. Proceeding this argument, we can find $x_n$ satisfying $\norm{y-T\sum\limits_{i=1}^n x_i}\leq r/2^{n+1}$. Since $X$ is complete and $\norm{\sum\limits_{i=n}^m x_i}\leq 2^{-n+1}$, it has convergent point $x$ and $\norm{x}\leq 1$ and $Tx=y$ since $\norm{Tx-y}=0$ in $Y$. Therefore, $T(B_1)$ contains all $y$ in $\norm{y}<r/2$.
\end{proof}
\begin{theorem}
(Closed Graph Theorem) If $X$ and $Y$ are Banach spaces and $T:X\rightarrow Y$ is a closed linear map, then $T$ is bounded.
\end{theorem}
\begin{proof}
Let $\pi_1$ and $\pi_2$ be the projection of $\Gamma(T)\coloneqq\{(x, Tx)\in X\times Y\}$ to $X$ and $Y$, then these maps are onto. It is clear that $\pi_1$ and $\pi_2$ are bounded linear functional. ALso, $X\times Y$ and $\Gamma(T)$ is complete since $X$ and $Y$ are complete and $\Gamma(T)$ is closed as $T$ is closed. Since $\pi_1$ is a bijection between $\Gamma(T)$ and $X$, $\pi_1^{-1}$ is continuous since $\pi_1$ bounded and continuous. Thus, $T=\pi_2\circ \pi_1^{-1}$ is bounded.
\end{proof}
If $\eta\in \rho(A)$, $A-\eta \text{Id}$ is one-to-one and onto by definition. Therefore, we can consider the inverse $(A-\eta \text{Id})^{-1}$. I'll first show that this is closed linear map.
\begin{enumerate}
\item[Linearity:] Fix $y_1, y_2\in X$ and $r\in \rr$ or $\mathbb{C}$. Then, there uniquely exists $x_1$ and $x_2$ in $X$ such that $(A-\eta \text{Id})(x_i)=y_i$ for each $i$ and $(A-\eta \text{Id})(rx_i)=ry_i$. Therefore, $(A-\eta \text{Id})^{-1}(y_i)=x_i$ and $(A-\eta \text{Id})^{-1}(y_1+ry_2)=x_1+rx_2$. Thus, $(A-\eta \text{Id})$ is bijective and linear.
\item[Closedness:] Suppose $y_n\rightarrow y$ in $X$ and $(A-\eta \text{Id})^{-1}(y_n)\rightarrow x$. We need to show that $(A-\eta \text{Id})^{-1}(y)=x$. The second assumption implies that $y_n\rightarrow (A-\eta \text{Id})(x)$ since $(A-\eta \text{Id})$ is continuous. (Note that boundedness implies continuity if $X$ is normed vector space and the map is linear.) The normed topology in Banach space gives Hausdorff property: if $x_1\neq x_2$, $r=\norm{x_1-x_2}>0$ and $B(x_1, r/3)$, $B(x_2, r/3)$ gives disjoint neighborhoods of each $x_i$. Therefore, $y_n$ converges to same point and $(A-\eta \text{Id})(x)=y$.
\end{enumerate}
Since $X$ is Banach space and $(A-\eta \text{Id})^{-1}:X\rightarrow X$ is closed linear map, it is bounded by the Closed Graph Theorem.
\section*{Problem 2}
\begin{enumerate}
\item[(a)] I'll check the condition for inner product.
\begin{enumerate}
\item[(1)] For all $u,u_*\in \mathcal{H}$,
\begin{equation*}
\begin{split}
\overline{(u_*,u)}_{\mathcal{H}}&=\overline{\int_\Omega (v_*+iw_*)(v-iw)+(Dv_*+iDw_*)(Dv-iDw)dx} \\
&=\int_\Omega (v_*-iw_*)(v+iw)+(Dv_*-iDw_*)(Dv+iDw)dx~~\text{since }v,w,v_*,w_*:X\rightarrow \mathbb{R} \\
&=(u, u_*)_{\mathcal{H}}.
\end{split}
\end{equation*}
\item[(2)] For $a,b\in \mathbb{C}$ and $u,u_*,u_{**}\in \mathcal{H}$,
\begin{equation*}
\begin{split}
(au+bu_*,u_{**})_{\mathcal{H}}&=\int_\Omega ((av+bv_*)+i(aw+bw_*))(v_{**}-iw_{**})\\
&+(D(av+bv_*)+iD(aw+bw_*))(Dv_{**}-iDw_{**})dx \\
&=a\int_\Omega (v+iw)(v_{**}-iw_{**})+(Dv+iDw)(Dv_{**}-iDw_{**})dx\\
&+b\int_\Omega (v_*+iw_*)(v_{**}-iw_{**})+(Dv_*+iDw_*)(Dv_{**}-iDw_{**})dx \\
&=a(u, u_{**})_{\mathcal{H}}+b(u_*, u_{**})_{\mathcal{H}}.
\end{split}
\end{equation*}
\item[(3)] For nonzero $u\in \mathcal{H}$,
\begin{equation*}
\begin{split}
(u,u)_{\mathcal{H}}&=\int_\Omega (v+iw)(v-iw)+(Dv+iDw)(Dv-iDw)dx \\
&=\int_\Omega v^2+w^2+\abs{Dv}^2+\abs{Dw}^2dx \\
&=\norm{v}^2_{H^1_0(\Omega)}+\norm{w}^2_{H^1_0(\Omega)}\in (0,\infty).
\end{split}
\end{equation*}
If both $\norm{v}^2_{H^1_0(\Omega)}$ and $\norm{w}^2_{H^1_0(\Omega)}$ are zero, $v=w=0$ in $H^1_0(\Omega)$ and it means $u=0$, which is contradiction.
\end{enumerate}
Therefore, $(\cdot,\cdot)_{\mathcal{H}}$ yields an inner product in $\mathcal{H}$.
\item[(b)] First, note that $\mathcal{H}$ is a Hilbert space.(First, $H^1_0(\Omega)$ is a Hilbert space as a closed subspace of Hilbert space $H^1(\Omega)$. Assume that $\{u_j\}_{j=1}^\infty$ is a Cauchy sequence in $\mathcal{H}$ about the norm defined above. By (3) in (a), $(u_i-u_j,u_i-u_j)_{\mathcal{H}}=\norm{\text{Re}(u_i-u_j)}^2_{H^1_0(\Omega)}+\norm{\text{Im}(u_i-u_j)}^2_{H^1_0(\Omega)}$ and both $\text{Re}(u_i-u_j)$ and $\text{Im}(u_i-u_j)$ are Cauchy sequence. Therefore, it has a convergent subsequence and $\mathcal{H}$ is a Hilbert space.)

I'll first show that the bilinear form $B$ is bounded.
\begin{enumerate}
\item[Bilinearity:] For $u_1,u_2,v_1,v_2\in \mathcal{H}$ and $c\in \mathbb{C}$,
\begin{equation*}
\begin{split}
B[cu_1+u_2,v_1]&=\int_\Omega a_{ij}\partial_i (cu_1+u_2)\partial \overline{v}_1~dx \\
&=c\int_\Omega a_{ij}\partial_i u_1\partial \overline{v}_1~dx+\int_\Omega a_{ij}\partial_i u_2\partial \overline{v}_1~dx \\
&=cB[u_1,v_1]+B[u_2,v_1]
\end{split}
\end{equation*}
and
\begin{equation*}
\begin{split}
B[u_1,cv_1+v_2]&=\int_\Omega a_{ij}\partial_i u_1\partial (c\overline{v}_1+\overline{v}_2)~dx \\
&=\overline{c}\int_\Omega a_{ij}\partial_i u_1\partial \overline{v}_1~dx+\int_\Omega a_{ij}\partial_i u_2\partial \overline{v}_1~dx \\
&=\overline{c}B[u_1,v_1]+B[u_2,v_1]
\end{split}
\end{equation*}
\item[Boundedness:]  For $u,v\in \mathcal{H}$,
\begin{equation*}
\begin{split}
\abs{B[u,v]}&=\abs{\int_\Omega a_{ij}\partial_i u\partial_j \overline{v}~dx} \\
&=\abs{\int_\Omega a_{ij}\partial_i (\text{Re}(u)+i\text{Im}(u))\partial_j (\text{Re}(v)-i\text{Im}(v))~dx} \\
&=\abs{\int_\Omega a_{ij} (\partial_i\text{Re}(u)\partial_j\text{Re}(v)-\partial_i\text{Im}(u)\partial_j\text{Im}(v)))~dx}\\
&+\abs{\int_\Omega a_{ij} (\partial_i\text{Re}(u)\partial_j\text{Im}(v)+\partial_i\text{Im}(u)\partial_j\text{Re}(v)))~dx}~~(*)\\
&\leq\int_\Omega \frac{1}{\mu} (\abs{D(\text{Re}(u))}\abs{D(\text{Re}(v))}+\abs{D(\text{Im}(u))}\abs{D(\text{Im}(v))})~dx\\
&+\int_\Omega \frac{1}{\mu} (\abs{D(\text{Re}(u))}\abs{D(\text{Im}(v))}+\abs{D(\text{Im}(u))}\abs{D(\text{Re}(v))})~dx\\
&=\frac{1}{\mu}\left(\norm{D(\text{Re}(u))}_{L^2(\Omega)}+\norm{D(\text{Im}(u))}_{L^2(\Omega)}\right)\left(\norm{D(\text{Re}(v))}_{L^2(\Omega)}+\norm{D(\text{Im}(v))}_{L^2(\Omega)}\right) \\
&\leq \frac{1}{\mu}\norm{u}_{\mathcal{H}}\norm{v}_{\mathcal{H}}.
\end{split}
\end{equation*}
In the middle step $(*)$, I used the diagonalizable of positive definite matrix of $A$: For unit vector $\eta_1\in \mathbb{R}^n$, it can be decomposed by the eigenvectors of $A$, so if
\begin{equation*}
\eta_1=\sum\limits_{i=1}^n b_i \xi_i
\end{equation*}
for unit eigenvectors of $A$ $\{\xi_i\}$, then
\begin{equation*}
A\eta_1 = \sum\limits_{i=1}^n\lambda_i b_i \xi_i
\end{equation*}
and, for unit vector $\eta_2\in \rr^n$ with decomposition $\eta_2= \sum\limits_{i=1}^n c_i \xi_i$,
\begin{equation*}
\eta_2^T A \eta_1=\sum\limits_{i=1}^n\lambda_i c_i b_i\leq \max\{\abs{\lambda_i}\}=\frac{1}{\mu}
\end{equation*}
since all the eigenvalues are not bigger than $\frac{1}{\mu}$ and are not smaller than $\mu>0$.

Therefore, it is bounded in $\mathcal{H}$. Fix $u\in \mathcal{H}$ and consider a bounded linear functional $T$ on $\mathcal{H}$ such that $T(v)=B[u,v]$ for all $v\in \mathcal{H}$. I can use the Riesz Representation Thereom and find a unique element $w\in \mathcal{H}$ satisfying
\begin{equation*}
B[u,v]=(w,v)_{\mathcal{H}}
\end{equation*}
for all $v\in \mathcal{H}$. It means we can find $w\in \mathcal{H}$ satisfying above for each $u\in \mathcal{H}$, so we can construct $\mathcal{L}:\mathcal{H}\rightarrow\mathcal{H}$ such that $\mathcal{L}(u)=w$. I need to show that this is bounded linear functional.
\begin{enumerate}
\item[Linearity:] For $\lambda_1,\lambda_2\in \mathbb{C}$, $u_1,u_2,v\in \mathcal{H}$,
\begin{equation*}
\begin{split}
(\mathcal{L}(\lambda_1 u_1+\lambda_2 u_2),v)_{\mathcal{H}}&=B[\lambda_1 u_1+\lambda_2 u_2,v]\\
&=\lambda_1 B[u_1,v]+\lambda_2 B[u_2,v]\\
&=\lambda_1 (\mathcal{L}(u_1),v)_{\mathcal{H}}+\lambda_2 (\mathcal{L}(u_2),v)_{\mathcal{H}}\\
&=(\lambda_1\mathcal{L}(u_1)+\lambda_2\mathcal{L}(u_2),v)_{\mathcal{H}}
\end{split}
\end{equation*}
for all $v\in \mathcal{H}$. By the uniqueness part of the Riesz Representation Theorem, $\mathcal{L}(\lambda_1 u_1+\lambda_2 u_2)=\lambda_1\mathcal{L}(u_1)+\lambda_2\mathcal{L}(u_2)$.
\item[Boundedness:] For $u\in \mathcal{H}$,
\begin{equation*}
\norm{\mathcal{L}u}^2_\mathcal{H}=(\mathcal{L}u,\mathcal{L}u)_{\mathcal{H}}=B[u, \mathcal{L}u]\leq \frac{1}{\mu}\norm{u}_{\mathcal{H}}\norm{\mathcal{L}u}_{\mathcal{H}}
\end{equation*}
Therefore, $\norm{\mathcal{L}u}_{\mathcal{H}}\leq \frac{1}{\mu}\norm{u}_{\mathcal{H}}$ and $\mathcal{L}$ is bounded.
\end{enumerate}
\item[(c)] First, $\mathcal{L}^*$ is well-defined since if $v_1=v_2$ in $\mathcal{H}$, $(u,\mathcal{L}^* v_1)=(\mathcal{L}u,v_1)=(\mathcal{L}u,v_2)=(u,\mathcal{L}^*v_2)$ for all $u\in \mathcal{H}$, so $\mathcal{L}^*v_1=\mathcal{L}^*v_2$.

Since $(a_{ij})$ is real valued and $a_{ij}=a_{ji}$, $B[u,v]=B[\overline{v},\overline{u}]=\overline{B[v,u]}$ as
\begin{equation*}
\begin{split}
B[\overline{u},\overline{v}]&=\int_\Omega a_{ij} \partial_i \overline{u}\partial_j v dx \\
&=\int_\Omega a_{ji} \partial_j v \partial_i \overline{u} dx \\
&=B[v,u]
\end{split}
\end{equation*}
Using this relation, for fixed $u\in\mathcal{H}$ and all $v\in \mathcal{H}$,
\begin{equation*}
\begin{split}
(\mathcal{L}^*u, v)_{\mathcal{H}}=\overline{(v,\mathcal{L}^*u)_{\mathcal{H}}}=\overline{(\mathcal{L}v,u)_{\mathcal{H}}}=\overline{B[v,u]}=B[\overline{v},\overline{u}] =B[u,v] =(\mathcal{L}u,v)_{\mathcal{H}}.
\end{split}
\end{equation*}
Therefore, $(\mathcal{L}u,v)_{\mathcal{H}}=(\mathcal{L}^*u,v)_{\mathcal{H}}$ for all $v$ and by uniqueness part of Riesz Representation Theorem again, $\mathcal{L}^*u=\mathcal{L}u$ for all $u\in \mathcal{H}$.(More precisely, we can define $T'v=(u,\mathcal{L}^*v)$ and since $Tv=T'v$, $T'$ is bounded linear operator, so by Riesz representation theorem, $\exists w'\in \mathcal{H}$ such that $(w',v)_\mathcal{H}=T'v$. Since $T'v=Tv$ for all $v$, $w'=w$ in $\mathcal{H}$.)
\item[(d)] Suppose $u$ is a nontrivial weak solution for the eigenvalue problem. By computing inner product;
\begin{equation*}
\int_\Omega (Lu)\overline{v}=\int_\Omega -\partial_j(a_{ij}\partial_i u)\overline{v}=\int_\Omega a_{ij}\partial_i u\partial_j \overline{v}=B[u,v]
\end{equation*}
for all $v\in \mathcal{H}$ since the real part and imaginary part of $u,v$ are in $H^1_0(\Omega)$. Therefore, we can define the condition of weak solution $u$ to satisfy
\begin{equation*}
B[u,v]=(\lambda u,v)_{L^2(\Omega)}
\end{equation*}
for all $v\in\mathcal{H}$. However,
\begin{equation*}
B[u,u]=(\mathcal{L}u,u)_{\mathcal{H}}=(\mathcal{L}^*u,u)_{\mathcal{H}}=(u,\mathcal{L}u)_{\mathcal{H}}=\overline{(\mathcal{L}u,u)_{\mathcal{H}}}=\overline{B[u,u]}
\end{equation*}
and it makes $\lambda(u,u)_{L^2(\Omega)}=(\lambda u,u)_{L^2(\Omega)}=\overline{(\lambda u,u)_{L^2(\Omega)}}=\overline{\lambda}\overline{(u,u)_{L^2(\Omega)}}$. The only case to consider is that $(u,u)_{L^2(\Omega)}\neq 0$. Assume that $(u,u)_{L^2(\Omega)}=0$, then $\norm{u}_{\mathcal{H}}=\norm{Du}_{H^1_0(\Omega)}>0$. However, it means
\begin{equation*}
\abs{B[u,u]}=\abs{\int_\Omega a_{ij}\partial_i u\partial_j \overline{u}~dx}\geq \mu \norm{Du}^2>0
\end{equation*}
which is contradiction since $B[u,u]=(\lambda u, u)_{L^2(\Omega)}=\lambda(u,u)_{L^2(\Omega)}=0$. Therefore, $\lambda\in \rr$.
\end{enumerate}
\end{enumerate}





\section*{Problem 3}
Since $u\in H^1(\Omega)$ is a weak solution to
\begin{equation*}
\begin{cases}
Lu=f & \text{in }\Omega \\
u=g & \text{in }\partial \Omega,
\end{cases}
\end{equation*}
for all $v\in H^1_0(\Omega)$,
\begin{equation*}
B[u,v]=\int_\Omega fv~dx
\end{equation*}
where the bilinear form $B[\cdot,\cdot]$ is defined by
\begin{equation*}
\int_\Omega \sum\limits_{i,j}a_{ij}\partial_i u \partial _j v + \sum\limits_{i}b_i v \partial_i u+cuv~dx.
\end{equation*}

I'll show the boundedness by contradiction. Assume that there exists $\{u'_k\}_{k=1}^\infty$, $\{f'_k\}$, $\{g'_k\}$ satisfying
\begin{equation*}
\norm{u'_k}_{L^2(\Omega)}>k\left(\norm{f'_k}_{L^2(\Omega)}+\norm{g'_k}_{H^1(\Omega)}\right)
\end{equation*}
and the boundary value problem. Let $u_k=\frac{u'_k}{\norm{u'_k}_{L^2(\Omega)}}$, $f_k=f'_k/{\norm{u'_k}_{L^2(\Omega)}}$, $g_k=g'_k/{\norm{u'_k}_{L^2(\Omega)}}$, then $u_k$ also satisfies the boundary value problem for $f_k$ and $g_k$ and the inequality
\begin{equation*}
\norm{u_k}_{L^2(\Omega)}>k\left(\norm{f_k}_{L^2(\Omega)}+\norm{g_k}_{H^1(\Omega)}\right).
\end{equation*}
Since $\norm{u_k}_{L^2(\Omega)}=1$ for all $k$, $\norm{f_k}_{L^2(\Omega)}, \norm{g_k}_{H^1(\Omega)}\rightarrow 0$ as $k\rightarrow \infty$. By a variation of energy estimation,
\begin{equation*}
\norm{u_k}^2_{H^1(\Omega)}\leq C\left(\norm{f_k}_{L^2(\Omega)}\norm{u_k}_{L^2(\Omega)}+\norm{u_k}^2_{L^2(\Omega)}\right)
\end{equation*}
for the constant $C$ not depending on $f_k$ and $u_k$.(By the ellipticity condition, there exists $\theta>0$ such that
\begin{equation*}
\begin{split}
\theta\int_\Omega \abs{Du}^2dx & \leq \int_\Omega a_{ij}\partial_i u\partial_j u dx \\
&=B[u,u]-\int_\Omega b_iu\partial_i u+cu^2 dx \\
&=B[u,u]+\sum\limits_{i}\norm{b_i}_{L^\infty}\int_\Omega \int_\Omega \abs{Du}\abs{u}dx+\norm{c}_{L^\infty}\int_\Omega u^2 dx
\end{split}
\end{equation*}
and by Cauchy's inequality,
\begin{equation*}
\int_\Omega \int_\Omega \abs{Du}\abs{u}dx\leq \epsilon\int_\Omega \abs{Du}^2 dx+\frac{1}{4\epsilon}\int_\Omega u^2 dx
\end{equation*}
for $\epsilon>0$. By choosing small enough $\epsilon$ to satisfy 
\begin{equation*}
\epsilon\sum\limits_{i} \norm{b_i}_{L^\infty}<\theta/2,
\end{equation*}
we get
\begin{equation*}
\frac{\theta}{2}\int_\Omega \abs{Du}^2 dx\leq B[u,u]+C\int_\Omega u^2 dx
\end{equation*}
for constant $C$. By adding $\frac{\theta}{2}\int_\Omega u^2 dx$ on both side, we get
\begin{equation*}
\norm{u}^2_{H^1(\Omega)}\leq C(B[u,u]+\norm{u}^2_{L^2(\Omega)})\leq C'\left(\norm{f_k}_{L^2(\Omega)}\norm{u_k}_{L^2(\Omega)}+\norm{u_k}^2_{L^2(\Omega)}\right)
\end{equation*}
which is the above inequality.)

Since $\norm{f_k}_{L^2(\Omega)}\rightarrow 0$ and $\norm{u_k}^2_{L^2(\Omega)}=1$, $\norm{u_k}_{H^1(\Omega)}$ is uniformly bounded. Therefore, by compact embedding theorem,(For $n>2$, we can use Rellich-Kondrachov Theorem and for $n=2$, we choose $p$ close enough to $n=2$ such that $2<p^*$ and as $H^1(\Omega)\subset W^{1,p}(\Omega)$, we again use Rellich-Kondrachov Theorem. For $n=1$, since $n<p=2$, it can be done by Morrey's inequality and Arzela-Ascoli compactness theorem, which was the last HW.) there exists subsequence $\{u_{k_j}\}_{j=1}^\infty$ such that
\begin{equation*}
\begin{cases}
u_{k_j}\rightharpoonup u & \text{weakly in }H^1(\Omega) \\
u_{k_j}\rightarrow u & \text{in }L^2(\Omega)
\end{cases}
\end{equation*}
where $u\in H^1(\Omega)$. (Note that $H^1(\Omega)$ is a Hilbert space and bounded sequence in it have weakly convergent subsequence.)

Since $\norm{u_{k_j}}_{L^2(\Omega)}=1$ for all $j$, $\norm{u}_{L^2(\Omega)}=1$. Also,
\begin{equation*}
\begin{cases}
\lim\limits_{k_j\rightarrow \infty}B[u_{k_j},\eta]=\lim\limits_{k_j\rightarrow \infty}(f_{k_j},\eta)_{L^2(\Omega)}=0 & \text{by }L^2\text{ convergence} \\
\lim\limits_{k_j\rightarrow \infty}B[u_{k_j},\eta]=B[u,\eta] & \text{by }H^1\text{ weak convergence}.
\end{cases}
\end{equation*}
for all $\eta\in H^1_0(\Omega)$. Therefore, $u$ is a nontrivial weak solution of the BVP:
\begin{equation*}
\begin{cases}
Lu=0 & \text{in }\Omega \\
u=0 & \text{in }\partial \Omega,
\end{cases}
\end{equation*}
However, this is impossible by the given condition. Therefore, there exists $C$ not depending on $u, f, g$ such that
\begin{equation*}
\norm{u}_{L^2(\Omega)}\leq C\left(\norm{f}_{L^2(\Omega)}+\norm{g}_{H^1(\Omega)}\right)
\end{equation*}
Also, by the above equation,
\begin{equation*}
\begin{split}
\norm{u}^2_{H^1(\Omega)}&\leq C\left(\norm{f}_{L^2(\Omega)}\norm{u}_{L^2(\Omega)}+\norm{u}^2_{L^2(\Omega)}\right) \\
&\leq C\left(\norm{f}_{L^2(\Omega)}\norm{u}_{H^1(\Omega)}+\norm{u}_{L^2(\Omega)}\norm{u}_{H^1(\Omega)}\right) \\
&\leq C'\left(\norm{f}_{L^2(\Omega)}+\norm{g}_{H^1(\Omega)}\right)\norm{u}_{H^1(\Omega)}
\end{split}
\end{equation*}
and
\begin{equation*}
\norm{u}_{H^1(\Omega)}\leq C\left(\norm{f}_{L^2(\Omega)}+\norm{g}_{H^1(\Omega)}\right)
\end{equation*}
where the constant $C$ not depending on $u,f,g$.




\section*{Problem 4}
\begin{enumerate}
\item[(a)] In the computation, I'll assume that $u,v$ are smooth function.
\begin{equation*}
\begin{split}
\int_\Omega -v\Laplace u+cuv~dx&=\int_\Omega -\sum\limits_{i=1}^n \partial_i (v\partial_i u)+\partial_i v \partial_i u+cuv~dx~\text{Integration by parts} \\
&=\int_{\partial \Omega} -\sum\limits_{i=1}^n \left(v\partial_i u\right)\nu^i dS+\int_\Omega -\partial_i v \partial_i u+cuv~dx~\text{Stokes' theorem} \\
&=\int_{\partial \Omega} v\nabla u \cdot \bm{\nu}_{\text{in}}dS+\int_\Omega \partial_i v \partial_i u+cuv~dx \\
&=\int_{\partial \Omega} gv~dS+\int_\Omega \partial_i v \partial_i u+cuv~dx \\
&=\int_\Omega fv~dx
\end{split}
\end{equation*}
for $u,v\in H^1(\Omega)$ and $\bm{\nu}_{\text{out}}=(\nu^1,\nu^2, \ldots, \nu^n)$ outward unit normal vector on $\partial \Omega$. Therefore, the definition of weak solution of this problem:
\begin{equation*}
B[u,v]=\int_\Omega \nabla u\cdot \nabla v + cuv~dx=\int_\Omega fv~dx-\int_{\partial \Omega} gv~dS
\end{equation*}
makes sense.
\item[(b)] First, note that $H^1(\Omega)$ is a Hilbert space. Define a bilinear form $B[\cdot,\cdot]$ by
\begin{equation*}
\int_\Omega \nabla u \cdot\nabla v + cuv~dx.
\end{equation*}
I'll show that this is well-defined elliptic form on $H^1(\Omega)$.
\begin{enumerate}
\item[Bilinear:] For $u_1,u_2,v_1, v_2\in H^1(\Omega)$ and $a\in \rr$ or $\mathbb{C}$,
\begin{equation*}
\begin{split}
B[au_1+u_2,v_1]&=\int_\Omega \nabla (au_1+u_2)\cdot \nabla v_1 + c(au_1+u_2)v_1~dx\\
&=a\int_\Omega \nabla u_1\cdot\nabla v_1 + c u_1v_1~dx+\int_\Omega \nabla u_2 \cdot\nabla v_1 + cu_2v_1~dx\\
&=aB[u_1,v_1]+B[u_2,v_1]
\end{split}
\end{equation*}
and
\begin{equation*}
\begin{split}
B[u_1,av_1+v_2]&=\int_\Omega \nabla u_1\cdot \nabla (av_1+v_2) + cu_1(av_1+v_2)~dx\\
&=a\int_\Omega \nabla u_1\cdot \nabla v_1 + cu_1v_1~dx+\int_\Omega \nabla u_1\cdot \nabla v_2 + cu_1v_2~dx\\
&=aB[u_1,v_1]+B[u_1,v_2]
\end{split}
\end{equation*}
\item[Boundedness:] For $u,v\in H^1(\Omega)$,
\begin{equation*}
\begin{split}
\abs{B[u,v]}&=\abs{\int_\Omega \nabla u \cdot\nabla v + cuv~dx} \\
&\leq\norm{Du}^{1/2}_{L^2(\Omega)}\norm{Dv}^{1/2}_{L^2(\Omega)}+\norm{c}_{L^\infty(\Omega)}\norm{u}_{L^2(\Omega)}\norm{v}_{L^2(\Omega)}\\
&\leq C(\norm{u}_{L^2(\Omega)}+\norm{Du}_{L^2(\Omega)})(\norm{v}_{L^2(\Omega)}+\norm{Dv}_{L^2(\Omega)}) \\
&=C\norm{u}_{H^1(\Omega)}\norm{v}_{H^1(\Omega)}
\end{split}
\end{equation*}
for constant $C$ depending only on $\Omega$ and $c$.
\item[Coercivity:] For $u\in H^1{\Omega}$,
\begin{equation*}
\begin{split}
B[u,u]&=\int_\Omega \nabla u \cdot\nabla u + cu^2~dx \\
&=\norm{Du}^2_{L^2(\Omega)}+\norm{c}_{L^\infty(\Omega)}\norm{u}^2_{L^2(\Omega)}\\
&\geq \min\{1,\mu_0\}\norm{u}^2_{H^1(\Omega)}
\end{split}
\end{equation*}
\end{enumerate}
Furthermore, define $I(f,g):H^1(\Omega)\rightarrow \rr$ by
\begin{equation*}
I:v\mapsto \int_{\Omega} fv~dx-\int_{\Omega} gv~dS.
\end{equation*}
Then, this is a bounded linear functional on $H^1(\Omega)$ since it is definitely linear and $I(v)=\abs{\int_{\Omega} fv~dx}+\abs{\int_{\Omega} gv~dS}\leq \norm{f}_{L^2(\Omega)}\norm{v}_{H^1(\Omega)}+C\norm{g}_{L^2(\partial \Omega)}\norm{v}_{H^1(\Omega)}$. (In the final step, I used trace inequality.)

By Lax-Millgram theorem, there exists a unique element $u\in H^1(\Omega)$ such that
\begin{equation*}
B[u,v]=I(v)
\end{equation*}
for all $v\in H^1(\Omega)$. Therefore, there exists unique weak solution to the boundary value problem.
\item[(c)] If $u\in H^1(\Omega)$ is a weak solution to the boundary value problem,
\begin{equation*}
\min\{1,\mu_0\}\norm{u}^2_{H^1(\Omega)}\leq \abs{B[u,u]}=\abs{I(u)}\leq \norm{f}_{L^2(\Omega)}\norm{u}_{H^1(\Omega)}+C\norm{g}_{L^2(\partial \Omega)}\norm{u}_{H^1(\Omega)}
\end{equation*}
so,
\begin{equation*}
\norm{u}_{H^1(\Omega)}\leq C'(\norm{f}_{L^2(\Omega)}+\norm{g}_{L^2(\partial \Omega)})
\end{equation*}
for some $C<C'$ constants depending only on $c,\Omega$.
\end{enumerate}



\section*{Problem 5}
$n=1$일 때 Boundary condition이 잘 안 맞고, $n=1$일 때 Boundary가 $C^\infty$라는 것이 non-sense라고 생각하여 $n\geq 2$를 가정하고 하였습니다.
\begin{enumerate}
\item[(a)] For $u,v\in H^1(\Omega)$,
\begin{enumerate}
\item[(i)]
\begin{equation*}
\begin{split}
(v,u)_{H^1}&=\int_\Omega \nabla u\cdot \nabla v~dx+\int_{\partial \Omega} uv~dS\\
&=\int_\Omega \nabla v\cdot \nabla u~dx+\int_{\partial \Omega} vu~dS \\
&=(u,v)_{H^1}
\end{split}
\end{equation*}
Therefore, $(u,v)_{H^1}=(v,u)_{H^1}$.
\item[(ii)] Since $\Omega$ is bounded and $\partial U$ is $C^\infty$, consider a trace operator, which is bounded linear operator,
\begin{equation*}
T:H^1(\Omega)\rightarrow L^2(\partial \Omega)
\end{equation*}
such that $Tu=u|_{\partial \Omega}$ for $u\in H^2(\Omega)\cap C(\bar{\Omega})$ and $\norm{Tu}_{L^2(\partial\Omega)}\leq C\norm{u}_{H^1(\Omega)}$ for all $u\in H^1(\Omega)$ with the constant $C$ only depending on $p$ and $\Omega$.
\begin{equation*}
\begin{split}
\abs{(u,v)_{H^1}}&=\abs{\int_\Omega \nabla u\cdot \nabla v~dx+\int_{\partial \Omega} uv~dS} \\
&\leq \int_\Omega \abs{Du}\abs{Dv}~dx+\int_{\partial \Omega} \abs{u}\abs{v}~dS \\
&\leq \norm{Du}_{L^2(\Omega)}\norm{Dv}_{L^2(\Omega)}+\norm{Tu}_{L^2(\Omega)}\norm{Tv}_{L^2(\Omega)}\\
&\leq C(\norm{Du}_{L^2(\Omega)}\norm{Dv}_{L^2(\Omega)}+\norm{u}_{H^1(\Omega)}\norm{v}_{H^1(\Omega)}) \\
&\leq C'(\norm{u}_{H^1(\Omega)}\norm{v}_{H^1(\Omega)})
\end{split}
\end{equation*}
for some $C, C'$ constant independent on $u,v$.
\item[(iii)] For nonzero $u\in H^1(\Omega)$,
\begin{equation*}
\begin{split}
(u,u)_{H^1}&=\int_\Omega \nabla u\cdot \nabla u~dx+\int_{\partial \Omega} u^2~dS\\
&=\norm{Du}^2_{L^2(\Omega)}+\norm{Tu}^2_{L^2(\partial \Omega)}<\infty
\end{split}
\end{equation*}
If $norm{Du}^2_{L^2(\Omega)}=\norm{Tu}^2_{L^2(\partial \Omega)}=0$, then $u\in H^1_0(\Omega)$ and if $n>2$, it means $\norm{u}_{H^1}=0$ since $\norm{u}_{L^2(\Omega)}\leq C\norm{Du}_{L^2(\Omega)}$ for constant $C$. For $n=2$, choose $p$ close enough to 2, then $\norm{u}_{L^2(\Omega)}\leq C\norm{Du}_{L^p(\Omega)}\leq C'\norm{Du}_{L^2(\Omega)}$. Therefore, $(\cdot,\cdot)_{H^1}$ is an inner product on $H^1(\Omega)$.(Linearity: For $a,b\in\rr$ and $u_1,u_2,v\in H^1(\Omega)$, $(au_1+bu_2,v)_{H^1}=\int_\Omega \nabla (au_1+bu_2)\cdot \nabla v~dx+\int_{\partial \Omega} (au_1+bu_2)v~dS=a\int_\Omega \nabla u_1\cdot \nabla v~dx+a\int_{\partial \Omega} u_1v~dS+b\int_\Omega \nabla u_2\cdot \nabla v~dx+b\int_{\partial \Omega} u_2v~dS=a(u_1,v)_{H^1}+b(u_2,v)_{H^1}$.) I need to show the coercivity.

I'll prove the coercivity by contradiction. Suppose there exists a sequence $\{u_k\}_{k=1}^\infty\subset H^1(\Omega)$ such that
\begin{equation*}
\norm{u_k}^2_{H^1(\Omega)}> k(u_k,u_k)_{H^1}.
\end{equation*}
For such $u_k$, take $v_k=u_k/\norm{u_k}_{H^1(\Omega)}$. Then, $\norm{v_k}_{H^1(\Omega)}=1$ and satisfies the above relation. As $k\rightarrow \infty$, $(v_k,v_k)_{H^1}\rightarrow 0$.

Since $\{v_k\}$ is a bounded sequence in $H^1(\Omega)$, which is compactly embedded in $L^2(\Omega)$, (I already explained how to deal for various dimension $n$ in Problem 3.) so there exists a subsequence $\{v_{k_j}\}_{j=1}^\infty$ such that 
\begin{equation*}
\begin{cases}
v_{k_j}\rightharpoonup v & \text{weakly in }H^1(\Omega) \\
v_{k_j}\rightarrow v & \text{in }L^2(\Omega)
\end{cases}
\end{equation*}
since $H^1(\Omega)$ is Hilbert space.(Since strong convergence implies weak convergence and weak limit in Hilbert space is unique. Therefore, the limit coincide in $L^2(\Omega)$.) As $v\in H^1(\Omega)$ and $\norm{v_{k_j}}_{H^1(\Omega)}=1$ for all $k_j$, $\norm{v}_{H^1(\Omega)}\leq 1$. Since $\norm{Dv_{k_j}}^2_{L^2(\Omega)}\leq (v_{k_j},v_{k_j})_{H^1}\leq \frac{1}{_{k_j}}$, $\norm{Dv_{k_j}}^2_{L^2(\Omega)}\rightarrow 0$ as $_{k_j}\rightarrow \infty$ and it means $\norm{v}_{L^2(\Omega)}=1$, $\norm{v}_{H^1(\Omega)}=0$ and $\norm{Dv}_{L^2(\Omega)}=0$. (If not, for some $N$, $\norm{v_N}^2_{H^1(\Omega)}=\norm{v_N}^2_{L^2(\Omega)}+\norm{Dv_N}^2_{L^2(\Omega)}<1$, which is contradiction.) Also,
\begin{equation*}
\norm{v_k-v}^2_{H^1(\Omega)}=\norm{v_{k_j}-v}^2_{L^2(\Omega)}+\norm{D(v_{k_j}-v)}^2_{L^2(\Omega)}\leq \norm{v_{k_j}-v}^2_{L^2(\Omega)}+\norm{Dv_{k_j}}^2_{L^2(\Omega)}+\norm{D(v_{k_j}-v)}^2_{L^2(\Omega)}\rightarrow 0
\end{equation*}
as ${k_j}\rightarrow \infty$, $v_{k_j}\rightarrow v$ in $H^1(\Omega)$.

Since $\norm{Tv_{k_j}}^2_{L^2(\partial \Omega)}\leq (v_{k_j},v_{k_j})_{H^1}<\frac{1}{k_j}$,
\begin{equation*}
\norm{Tv}_{L^2(\partial \Omega)}\leq \norm{T(v-v_{k_j})}_{L^2(\partial \Omega)}+\norm{Tv_{k_j}}_{L^2(\partial \Omega)}\leq \frac{1}{\sqrt{k_j}}+C\norm{v-v_{k_j}}_{H^1(\Omega)}
\end{equation*}
where the $C$ is given by the Trace Theorem. Therefore, $\norm{Tv}_{L^2(\partial \Omega)}=0$.

Summarising the fact, $v\in H^1(\Omega)$ and $Tv=0$ on $\partial \Omega$, so $v\in H^1_0(\Omega)$ and $\norm{Dv}_{L^2(\Omega)}=0$. For $n>2$, $\norm{v}_{L^2(\Omega)}\leq C\norm{Dv}_{L^2(\Omega)}$ for the constant $C$ depending only on $n$, and $\Omega$, so $\norm{v}_{L^2(\Omega)}=0$. For $n=2$, we can find $p$ near to $2$ and get $\norm{v}_{L^2(\Omega)}\leq C\norm{Dv}_{L^p(\Omega)}$. Since $\norm{Dv}_{L^2(\Omega)}=0\Rightarrow \norm{Dv}_{L^p(\Omega)}=0$, $\norm{v}_{L^2(\Omega)}=0$. Therefore, $\norm{v}_{L^2(\Omega)}=0$ also in $n=1$ case. Finally, this result shows that $v=0$, but $\norm{v}_{H^1(\Omega)}\neq 0$, which is contradiction.

Thus, there exists $C$ not depending on $u\in H^1(\Omega)$ such that
\begin{equation*}
\norm{u}^2_{H^1(\Omega)}\leq C(u,u)_{H^1}.
\end{equation*}
\end{enumerate}
\item[(b)] I'll rewrite $(u,v)_{H^1}$ by $B[u,v]$. Consider a BVP:
\begin{equation*}
\begin{cases}
-\Laplace u=f & \text{in }\Omega\\
\nabla u\cdot \bm{n}_{\text{in}}-u=0 & \text{on }\partial \Omega
\end{cases}
\end{equation*}
for $f\in L^2(\Omega)$. Then, the weak solution of the BVP should satisfy
\begin{equation*}
B[u,v]=\int_\Omega f v~dx
\end{equation*}
for all $v\in H^1(\Omega)$. (This result is from problem 4 (a).)

Assume that there exists eigenvalue $\lambda$ and the corresponding nontrivial weak solution $u\in H^1(\Omega)$. Then, for all $v\in H^1(\Omega)$,
\begin{equation*}
B[u,v]=(\lambda u, v)_{L^2(\Omega)}
\end{equation*}
If we put $u$ as $v$,
\begin{equation*}
B[u,u]=(\lambda u, u)_{L^2(\Omega)}=\lambda\norm{u}_{L^2(\Omega)}>0
\end{equation*}
since $\norm{u}_{H^1(\Omega)}>0$. If $\lambda$ is not real, it is nonsense. Also, if $\lambda\leq 0$, it is contradiction to coercivity of $B$. Therefore, every eigenvalue of (EVP) is a positive real.
\item[(c)] Since $B$ is symmetric bounded linear function with coercivity, By the Lax-Millgram Theorem, there exists unique weak solution $u\in H^1(\Omega)$ to the BVP for each $f$. Let's define $L^{-1}:L^2(\Omega)\rightarrow L^2(\Omega)$ by sending $f$ to $u$. Now, I claim that $L^{-1}$ is bounded, linear, compact operator. It is linear since if $L^{-1}(f_1)=u_1$ and $L^{-1}(f_2)=u_2$, then the unique weak solution to $rf_1+f_2$ is $ru_1+u_2$ for $r\in \rr$ and $L^{-1}(rf_1+f_2)=ru_1+u_2$. Also, $L^{-1}$ is bounded. It requires same argument used in problem 3. If there is no constant $C$ such that $\norm{u}_{L^2(\Omega)}\leq C\norm{f}_{L^2(\Omega)}$, there is a nontrivial weak solution to
\begin{equation*}
\begin{cases}
Lu=0 & \text{in }\Omega\\
\nabla u\cdot \bm{n}_{\text{in}}-u=0 & \text{on }\partial \Omega
\end{cases}
\end{equation*}
and since we just showed that $\lambda=0$ can not be an eigenvalue, this is impossible. Finally, $L^{-1}$ is compact: if $\{f_k\}_{k=1}^\infty$ is uniformly bounded in $L^2(\Omega)$ and let $u_k=L^{-1}f_k$, then by coercivity, there exists $\beta>0$ such that $\beta\norm{u_k}^2_{H^1(\Omega)} \leq B[u_k,u_k]=(f_k,u_k)_{L^2(\Omega)}\leq \norm{f_k}_{L^2(\Omega)}\norm{u_k}_{H^1(\Omega)}$ and $\norm{u_k}_{H^1(\Omega)}\leq C$ for all $k$. By Rellich-Kondrachov Compactness Theorem (and for $n=2,1$ cases as described in previous) there exists $u_k\rightarrow u $ in $L^2(\Omega)$ and it means $L^{-1}$ is compact.


$u$ is a weak solution of the EVP in the problem if and only if $L^{-1}(\lambda u)=u$ if and only if $u-\lambda L^{-1}u=0$. Since $\lambda>0$, we can denote $\left(L^{-1}-\frac{1}{\lambda}\text{Id}\right)u=0$. Therefore, $\lambda\in \Sigma$ if and only if $\frac{1}{\lambda}\in \sigma_p(L^{-1})\setminus\{0\}$ and $\Sigma=\left\{\lambda\in \rr\mid \frac{1}{\lambda}\in \sigma_p\left(L^{-1}\right)\setminus\{0\}\right\}$.

Since $L^{-1}:L^2(\Omega)\rightarrow L^2(\Omega)$ and $L^2(\Omega)$ separable as the domain of the function is open set $\Omega\subset \rr^n$.
Also, $L^{-1}$: symmetric: Fix $f,g\in L^2(\Omega)$ and let $\omega=L^{-1}f$, $\xi=L^{-1}g$, then $\omega,\xi\in H^1(\Omega)$ and
\begin{equation*}
\begin{split}
(L^{-1}f, g)_{L^2(\Omega)}&=\int_\Omega g\omega dx\\
&=\int_\Omega \nabla \xi\cdot \nabla \omega dx+\int_{\partial \Omega} \xi \omega dS \\
&=\int_\Omega \nabla \omega\cdot \nabla \xi dx+\int_{\partial \Omega} \omega\xi dS \\
&=\int_\Omega f \xi dx \\
&=(f, L^{-1}g).
\end{split}
\end{equation*}
Therefore, there exists countable orthonormal basis of $L^2(\Omega)$ consisting of eigenvectors of $L^{-1}$. By Fredholm alternative, the dimension of null space of $\left(\text{Id}-\lambda L^{-1}\right)$ for $\lambda\in \Sigma$ is finite. Therefore, $\abs{\Sigma}=\infty$. Since $L^{-1}$ is compact and the dimension of $L^2(\Omega)$ is infinite, $\sigma(L^{-1})\setminus\{0\}=\sigma_p(L^{-1})\setminus\{0\}$ and $\sigma(L^{-1})\setminus\{0\}$ is a sequence tending to $0$. Therefore, $\Sigma$ consists of the eigenvalues monotonic increasing to $\infty$.
\item[(d)] In the (c), I showed that there exists countable orthonormal basis of separable space $L^2(\Omega)$ consisting of eigenvectors of compact and symmetric bounded linear operator $L^{-1}$. I need to show that this is orthogonal basis of $H^1(\Omega)$.
\begin{equation*}
B[w_i,w_j]=(Lw_i, w_j)_{L^2(\Omega)}=(Lw_j, w_i)_{L^2(\Omega)}=B[w_j,w_i]
\end{equation*}
If $i\neq j$, $(Lw_i, w_j)_{L^2(\Omega)}=\lambda_i (w_i,w_j)_{L^2(\Omega)}=0$. If $i=j$, $(Lw_i, w_i)_{L^2(\Omega)}=\lambda_i$. 

Finally, assume that $\{w_i\}$ can not span $H^1(\Omega)$. Then, there exists nontrivial $\xi\in H^1(\Omega)$ such that $B[w_i,\xi]=0$ for all $w_i$. Then, $B[w_i, \xi]=(\lambda_i w_i, \xi)_{L^2(\Omega)}=0$ and $\lambda_i>0$ for all $i$. Therefore, $\xi=0$, which is contradiction. Therefore, $\{w_i\}$ spans $H^1(\Omega)$.
Thus, $\{w_i\}$ forms a orthogonal basis of $H^1(\Omega)$.
\end{enumerate}
\section*{Problem 6}
\begin{enumerate}
\item[(Step 1)] In problem 5 (d), we found a set of functions $\{w_k\}_{k=1}^\infty\subset H^1(\Omega)\cap C^\infty (\Omega)$ such that
\begin{enumerate}
\item[(i)] $\{w_k\}$ forms an orthornormal basis of $L^2(\Omega)$, and
\item[(ii)] $\{w_k\}$ forms an orthogonal basis of $H^1(\Omega)$ with respect to the inner product $(\cdot,\cdot)_{H^1}=B[\cdot,\cdot]$.

The weak solution of (IBVP-P) should satisfies
\begin{equation*}
(u'(t),v)_{L^2(\Omega)}+B[u(t),v]=(f(t),v)_{L^2(\Omega)}
\end{equation*}
for $v\in H^1(\Omega)$ and a.e. time $0\leq t\leq T$ and $u(0)=g$.
\end{enumerate}
\item[(Step 2)] I'll use Galerkin approximation. Fix $m\in \mathbb{N}$ and set $u_m(t,x)=\sum\limits_{k=1}^m d_k(t)w_k(x)$. I need to find $\{d_k\}_{k=1}^m$ satisfying
\begin{enumerate}
\item[(i)] $(u_m'(t,\cdot),w_k)_{L^2(\Omega)}+B[u_m(t), w_k]=(f(t,\cdot), w_k)_{L^2(\Omega)}$ for $1\leq j\leq m$.
\item[(ii)] $u_m(0,x)=\sum\limits_{k=1}^m d_k(0)w_k(x)=g^{(m)}(x)$ where $g^{(m)}(x)=\sum\limits_{k=1}^m G_k w_k(x)$, $G_k=(g, w_k)_{L^2(\Omega)}$.
\end{enumerate}
Note that $u_m$ satisfies boundary condition $\nabla u_m\cdot \bm{n}_{\text{in}}-u_m=0$ on $(0,T]\times \partial \Omega$ since $w_k=0$ on $\partial \Omega$ for all $k$.

Define $f^{(m)}(t,x)\coloneqq \sum\limits_{k=1}^m F_k(t)w_k(x)$ where $F_k(t)=(f(t, \cdot),w_k)_{L^2(\Omega)}$.

Note that (i) holds if and only if $d'_j(t)+\lambda_j d_j(t)=F_j(t)$ for $0<t\leq T$ and $1\leq j\leq m$, and (ii) holds if and only if $d_j(0)=G_j=(g,w_j)_{L^2(\Omega)}$:
\begin{equation*}
(\sum\limits_{k=1}^m d'_k(t)w_k(x),w_j)_{L^2(\Omega)}+B[\sum\limits_{k=1}^m d_k(t)w_k(x), w_j]=(f(t,\cdot), w_j)_{L^2(\Omega)}\Leftrightarrow d'_j(t)+\lambda_j d_j(t)=F_j(t)
\end{equation*}
and
\begin{equation*}
\begin{split}
\sum\limits_{k=1}^m d_k(0)w_k(x)&=\sum\limits_{k=1}^m G_k w_k(x) \\
&\Leftrightarrow \left(\sum\limits_{k=1}^m d_k(0)w_k(x), w_j(x)\right)_{L^2(\Omega)}=\left(\sum\limits_{k=1}^m G_k w_k(x), w_j(x)\right)_{L^2(\Omega)}~\text{For all }1\leq j\leq m \\
&\Leftrightarrow d_j(0)=G_j~\text{For all }1\leq j\leq m
\end{split}
\end{equation*}
Since each $F_j(t),G_j(t)$ are smooth, by the uniqueness existence of ODEs, the initial value problem for each $j$:
\begin{equation*}
\begin{cases}
d'_j(t)+\lambda_j d_j(t)=F_j(t) & 0<t\leq T\\
d_j(0)=G_j=(g,w_j)_{L^2(\Omega)}
\end{cases}
\end{equation*}
has a unique smooth solution $d_j$ for $1\leq j\leq m$. With these $d_j$, $u_m(t,x)=\sum\limits_{k=1}^m d_k(t)w_k(t)$ satisfies (i),(ii) and $0$ on $(0,T]\times \partial \Omega$.

What I want is that as $m\rightarrow \infty$, $u_m\rightarrow u\in L^2((0,T);H^1(\Omega)	)$, $u'\in L^2((0,T);H^1_*(\Omega))$.

For now, I'll accept the proposition:
\begin{proposition}
For each $u_m$ satisfies
\begin{equation*}
\max_{t\in [0,T]}\norm{u_m(t)}_{L^2(\Omega)}+\norm{u_m(t)}_{L^2(0, t;H^1(\Omega))}+\norm{u'_m}_{L^2(0,T;H	_*^1(\Omega))}\leq C\left(\norm{f}_{L^2(0,T;L^2(\Omega))}+\norm{g}_{L^2(\Omega)}\right)
\end{equation*}
for some constant $C$ depending only on $\Omega,T$.
\end{proposition}
\item[(Step 3)]
By the proposition, we get the fact that $\{u_m\}$ is uniformly bounded in $L^2(0,T;H^1(\Omega))$ and $\{u'_m\}$ is uniformly bounded in $L^2(0,T;H	_*^1(\Omega))$. Since $L^2(0,T;H^1(\Omega))$ and $L^2(0,T;H	_*^1(\Omega))$ are Hilbert space since $L^2(0,T)$ is, there is a subsequence such that
\begin{equation*}
\begin{cases}
u_{m_k}\rightharpoonup u & \text{in }L^2(0,T;H^1(\Omega)) \\
u'_{m_k}\rightharpoonup u' & \text{in }L^2(0,T;H	_*^1(\Omega))
\end{cases}
\end{equation*}
(We know that $u'_{m_k}\rightharpoonup w\in L^2(0,T;H	_*^1(\Omega))$. I'll show that $u'=w$. For $\phi\in C^\infty_c(0,T)$ and $v\in H^1(\Omega)$,
\begin{equation*}
\begin{split}
\langle \int_0^T \phi'(t)u(t) dt,v\rangle&=\int_0^T  \langle \phi'(t)u(t), v\rangle dt =\int_0^T  \langle u(t), \phi'(t)v\rangle dt\\
&=\int_0^T  \lim\limits_{m_k\rightarrow\infty}\langle u_{m_k}(t), \phi'(t)v\rangle dt =\lim\limits_{m_k\rightarrow\infty}\int_0^T \langle u_{m_k}(t), \phi'(t)v\rangle dt \\
&=\lim\limits_{m_k\rightarrow\infty}\langle\int_0^T  u_{m_k}(t)\phi'(t) dt, v\rangle =\lim\limits_{m_k\rightarrow\infty}\langle\int_0^T  u'_{m_k}(t)\phi(t) dt, v\rangle \\
&=\int_0^T  \lim\limits_{m_k\rightarrow\infty}\langle u'_{m_k}(t), \phi(t)v\rangle dt =\int_0^T \langle w(t), \phi(t)v\rangle dt \\
&=\langle\int_0^T  w(t)\phi(t) dt, v\rangle.
\end{split}
\end{equation*}
The $\langle\cdot,\cdot,\rangle$ represent the action of $H^1_*(\Omega)$ to $H^1(\Omega)$ and the commutativity of $\langle\cdot,\cdot,\rangle$ and integral is by smoothness of $\phi$ and riemann sum argument. The commutativity of limit and integral is by the boundedness of $U$ and $(0,T)$ and integrability of $u,v,\phi$ with dominance convergence theorem. Therefore, $u'=w$.)

Now, I'll show that $u$ is the weak solution to (IBVP-P). 

Since $\nabla u_{m_k}\cdot \bm{n}_{\text{in}}-u_{m_k}=0$ on $(0,T]\times \partial \Omega$ for all $m_k$, $\nabla u\cdot \bm{n}_{\text{in}}-u=0$ on $(0,T]\times \partial \Omega$.

Fix $N\in \mathbb{N}$ and fix $m_k\geq N$. Consider $u_{m_k}=\sum\limits_{i=1}^{m_k} d_i(t)w_i(x)$. Fix $j\in\{1,\cdots, N\}$ and let $\alpha(t)$ be a smooth function. Then,
\begin{equation*}
\begin{split}
&\int_0^T \alpha(s)\left((u'_{m_k}(s),w_j)_{L^2(\Omega)}+B[u_{m_k}(s),w_j]\right)ds=\int_0^T (f^{(m_l)}(t),w_j)_{L^2(\Omega)}\alpha(s)ds \\
&\Leftrightarrow \int_0^T (u'_{m_k}(s),\alpha(s)w_j)_{L^2(\Omega)}+B[u_{m_k}(s),\alpha(s)w_j]ds=\int_0^T (f^{(m_k)}(t),w_j)_{L^2(\Omega)}\alpha(s)ds
\end{split}
\end{equation*}
By the weak convergence, as $m_k\rightarrow \infty$,
\begin{equation*}
\int_0^T (u'(s),\alpha(s)w_j)_{L^2(\Omega)}+B[u(s),\alpha(s)w_j]ds=\int_0^T (f(t),w_j)_{L^2(\Omega)}\alpha(s)ds
\end{equation*}
Since $\alpha(s)$ is arbitrary, we can let $\alpha(s)\rightarrow \delta(s-t)$ (such as standard mollifier) and get
\begin{equation*}
(u'(t),w_j)_{L^2(\Omega)}+B[u(t),w_j]=(f(t),w_j)_{L^2(\Omega)}
\end{equation*}
Since $N$ is arbitrarily fixed, this is true for all $j$. Since the function $\sum\limits_{i=1}^n d_i(x)w_i(x)$ with coefficient $d_i(x)\in H^1(\Omega)$ is dense in $H^1(\Omega)$, we get
\begin{equation*}
(u'(t),v)_{L^2(\Omega)}+B[u(t),v]=(f(t),v)_{L^2(\Omega)}
\end{equation*}
for $v\in H^1(\Omega)$ and a.e. time $0\leq t\leq T$.

I still need to check the initial condition. For the same circumstance with one more condition $\alpha(T)=0$,
\begin{equation*}
\begin{split}
&\int_0^T (u'(s),\alpha(s)w_j)_{L^2(\Omega)}+B[u(s),\alpha(s)w_j]ds=\int_0^T (f(t),w_j)_{L^2(\Omega)}\alpha(s)ds \\
&\Rightarrow \int_0^T -(u(s),(\alpha(s)w_j)')_{L^2(\Omega)}+B[u(s),\alpha(s)w_j]ds=\int_0^T (f(t),w_j)_{L^2(\Omega)}\alpha(s)ds+(u(0),\alpha(0)w_j))
\end{split}
\end{equation*}
and
\begin{equation*}
\begin{split}
&\int_0^T (u'_{m_k}(s),\alpha(s)w_j)_{L^2(\Omega)}+B[u_{m_k}(s),\alpha(s)w_j]ds=\int_0^T (f^{(m_k)}(t),w_j)_{L^2(\Omega)}\alpha(s)ds \\
&\Rightarrow \int_0^T -(u_{m_k}(s),(\alpha(s)w_j)')_{L^2(\Omega)}+B[u_{m_k}(s),\alpha(s)w_j]ds=\int_0^T (f^{(m_k)}(t),w_j)_{L^2(\Omega)}\alpha(s)ds+(u_{m_k}(0),(\alpha(0)w_j)).
\end{split}
\end{equation*}
Letting $m_k\rightarrow\infty$ and by weak convergence,
\begin{equation*}
\int_0^T -(u(s),(\alpha(s)w_j)')_{L^2(\Omega)}+B[u(s),\alpha(s)w_j]ds=\int_0^T (f(t),w_j)_{L^2(\Omega)}\alpha(s)ds+(g(0),(\alpha(0)w_j))
\end{equation*}
as $u_{m_k}(0)=g^{(m_k)}$ and $\lim\limits_{m_k\rightarrow\infty} u_{m_k}(0)=\lim\limits_{m_k\rightarrow\infty}g^{(m_k)}=g$. This is true for all $\alpha\in C^\infty((0, T))$ and for all $j$, $u(0)=g(0)$.

The left one is to show the proposition. For readability, I again write the proposition:

For each $u_m$ satisfies
\begin{equation*}
\max_{t\in [0,T]}\norm{u_m(t)}_{L^2(\Omega)}+\norm{u_m(t)}_{L^2(0, t;H^1(\Omega))}+\norm{u'_m}_{L^2(0,T;H	_*^1(\Omega))}\leq C\left(\norm{f}_{L^2(0,T;L^2(\Omega))}+\norm{g}_{L^2(\Omega)}\right)
\end{equation*}
for some constant $C$ depending only on $\Omega,T$.

I'll start from this equation:
\begin{equation*}
(\sum\limits_{k=1}^m d'_k(t)w_k(x),w_j)_{L^2(\Omega)}+B[\sum\limits_{k=1}^m d_k(t)w_k(x), w_j]=(f(t,\cdot), w_j)_{L^2(\Omega)}
\end{equation*}
Note that $d_k(t)$ are calculated for fixed $m$. On each side for fixed $j$, multiply $d_j(t)$ and sum about $j$, then we get
\begin{equation*}
(u'_m(t),u_m(t))_{L^2(\Omega)}+B[u_m(t), u'_m(t)]=(f(t,\cdot), u_m(t))_{L^2(\Omega)}
\end{equation*}
for a.e. $0\leq t\leq T$. For fixed $t\in [0,T]$, $(u'_m,u_m)_{L^2(\Omega)}=\frac{d}{dt}\left(\frac{1}{2}\norm{u_m}^2_{L^2(\Omega)}\right)$ and $\abs{(f,u_m)}\leq \frac{1}{2}\norm{f}^2_{L^2(\Omega)}+\frac{1}{2}\norm{u_m}^2_{L^2(\Omega)}$. Furthermore, I'll use the proof of variation of energy estimation used in problem 3: there exists $\beta,\gamma>0$ such that
\begin{equation*}
\beta\norm{u_m}^2_{H^1(\Omega)}\leq B[u_m, u_m, t]+\gamma \norm{u_m}^2_{L^2(\Omega)}.
\end{equation*}
Mixing these inequalities, we get
\begin{equation}\label{Eq:6-1}
\frac{d}{dt}\left(\norm{u_m}^2_{L^2(\Omega)}\right)+2\beta\norm{u_m}^2_{H^1(\Omega)}\leq C_1\norm{u_m}^2_{L^2(\Omega)}+C_2\norm{f}^2_{L^2(\Omega)}.
\end{equation}
for a.e. $0\leq t\leq T$ and constant $C_1,C_2$ not depending on $u_m, f$.

Now, let 
\begin{equation*}
\eta(t)\coloneqq \norm{u_m(t)}^2_{L^2(\Omega)}
\end{equation*}
and
\begin{equation*}
\xi(t)\coloneqq \norm{f(t)}^2_{L^2(\Omega)}.
\end{equation*}
Then,
\begin{equation*}
\eta'(t)\leq C_1\eta(t)+C_2\xi(t)
\end{equation*}
for a.e. $0\leq t\leq T$ and by differential form of Gronwall's inequality,
\begin{equation*}
\eta(t)\leq e^{C_1t}\left(\eta(0)+C_2\int_0^t\xi(s)ds\right)
\end{equation*}
for $0\leq t\leq T$. Since $\eta(0)=\norm{u_m(0)}^2_{L^2(\Omega)}\leq \norm{g}^2_{L^2(\Omega)}$, (Note that $u_m(0)$ is the projection of $g$.)
\begin{equation*}
\max_{t\in[0,T]}\norm{u_m(t)}^2_{L^2(\Omega)}\leq C\left(\norm{g}^2_{L^2(\Omega)}+\norm{f}^2_{L^2(0, T; L^2(\Omega))}\right).
\end{equation*}
Also, integrating \eqref{Eq:6-1} from $0$ to $T$ generates the relation:
\begin{equation*}
\norm{u_m}^2_{L^2(0,T;H^1(\Omega))}=\int_0^T \norm{u_m}^2_{H^1(\Omega)}dt\leq C\left(\norm{g}^2_{L^2(\Omega)}+\norm{f}^2_{L^2(0, T; L^2(\Omega))}\right)
\end{equation*}
Finally, I'll estimate $\norm{u'_m}_{L^2(0,T;H^1_*(\Omega)}$. Fix $v\in H^1(\Omega)$ with $\norm{v}_{H^1(\Omega)}\leq 1$ and denote $v=v^1+v^2$ by $v_1\in \text{span}\left(\{w_i\}_{i=1}^m\right)$ and $(v_2,w_i)=0$ for $i\in \{1, \ldots, m\}$. Since $v_1$ is the projection to $\text{span}\left(\{w_i\}_{i=1}^m\right)$, $\norm{v^1}_{H^1(\Omega)}\leq \norm{v}_{H^1(\Omega)}\leq 1$. Using the previous equation: $(u_m'(t,\cdot),w_k)_{L^2(\Omega)}+B[u_m(t), w_k]=(f(t,\cdot), w_k)_{L^2(\Omega)}$, we can write
\begin{equation*}
(u_m'(t,\cdot),v^1)_{L^2(\Omega)}+B[u_m(t), v^1]=(f(t,\cdot), v^1)_{L^2(\Omega)}
\end{equation*}
for a.e. $0\leq t\leq T$. Since $u'_m\in \text{span}\left(\{w_i\}_{i=1}^m\right)$,
\begin{equation*}
(u'_m,v)_{L^2(\Omega)}=(u'_m,v^1)_{L^2(\Omega)}=(f,v^1)-B[u_m(t),v^1].
\end{equation*}
Therefore,
\begin{equation*}
\abs{(u'_m, v)_{L^2(\Omega)}}\leq C\left(\norm{f}_{L^2(\Omega)}+\norm{u_m}_{H^1(\Omega)}\right)
\end{equation*}
since $\norm{v^1}_{H^1(\Omega)}\leq 1$.(Also, by boundedness of $B[\cdot,\cdot]$: $\abs{B[u_m,v^1;t]}\leq \theta \norm{u_m(t)}_{H^1(\Omega)}$ for some constant $\theta$.) Since $\norm{v}_{H^1(\Omega)}=1$ and RHS is independent to $v$, 
\begin{equation*}
\norm{u'_m}_{H^1_*(\Omega)}\leq C\left(\norm{f}_{L^2(\Omega)}+\norm{u_m}_{H^1(\Omega)}\right)
\end{equation*}
and
\begin{equation*}
\norm{u'_m}_{L^2(0,T;H^1_*(\Omega))}=\int_0^T \norm{u'_m}_{H^1_*(\Omega)}\ dt\leq C'\left(\norm{g}_{L^2(\Omega)}+\norm{f}_{L^2(0,T;L^2(\Omega))}\right)
\end{equation*}
for some constant $C'$.(Note that we already showed that $\norm{u_m}^2_{L^2(0,T;H^1(\Omega)}$ is bounded by $\norm{g}_{L^2(\Omega)}$ and $\norm{f}_{L^2(0,T;L^2(\Omega))}$.
\end{enumerate}
Summarizing all the results, we get
\begin{equation*}
\max_{t\in [0,T]}\norm{u_m(t)}_{L^2(\Omega)}+\norm{u_m(t)}_{L^2(0, t;H^1(\Omega))}+\norm{u'_m}_{L^2(0,T;H	_*^1(\Omega))}\leq C\left(\norm{f}_{L^2(0,T;L^2(\Omega))}+\norm{g}_{L^2(\Omega)}\right)
\end{equation*}
for some $C$. This is true for all $m$ since the estimation constant does not depending on $u_m, f, g$.
\end{document}